Understanding meta-analysis through data simulation with applications to power analysis

### 2023-09-11 documents/paper/paper.Rmd
fixing intro and wordcount

keywords          : "meta-analysis, monte carlo simulations, power analysis"
wordcount         : "7866"
bibliography      : "../files/references.bib"
floatsintext      : yes
figsintext        : yes
linenumbers       : "`r params$linenumbers`"
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
numbersections    : false
nocite: |
  @r-lang
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1,footnotesize}}
  - \usepackage{float}
  - \usepackage{orcidlink}
  - \newcommand{\rev}[1]{\textcolor{red}{#1}}
documentclass     : "apa6"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex
params: 
  linenumbers: "yes"
  finalsection: TRUE
---

@@

The aim of the tutorial is not providing a complete theoretical introduction to meta-analysis but presenting the core topics using a simulation-based approach. Readers expert in conducting meta-analyses could benefit more from the proposed approach in terms of simulation setup and coding strategies. Readers without experience in meta-analysis could benefit both from the theoretical introduction and the simulation approach. However, for a better and extensive overview of meta-analysis topics the reader could refer to meta-analysis textbooks [e.g., @Harrer2019-rl; @Borenstein2009-mo].

>>>>

keywords          : "meta-analysis, monte carlo simulations, power analysis"
wordcount         : 7869
bibliography      : "../files/references.bib"
floatsintext      : yes
figsintext        : yes
linenumbers       : "`r params$linenumbers`"
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
numbersections    : false
nocite: |
  @r-lang
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1,footnotesize}}
  - \usepackage{float}
  - \usepackage{orcidlink}
  - \newcommand{\rev}[1]{\textcolor{red}{#1}}
documentclass     : "apa6"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex
params: 
  linenumbers: "yes"
  finalsection: TRUE
---

@@

The aim of the tutorial is not to provide a complete theoretical introduction to meta-analysis but rather to present core topics using a simulation-based approach. Readers experienced in conducting meta-analyses can benefit from the proposed approach in terms of simulation setup and coding strategies. Readers without prior experience in meta-analysis can benefit both from the theoretical introduction and the simulation approach. However, for a more comprehensive overview of meta-analysis topics the reader may refer to meta-analysis textbooks [e.g., @Harrer2019-rl; @Borenstein2009-mo]
